\documentclass[12pt,a4paper]{moderncv}

%----------------------------------------------------------
% Style configuration
%----------------------------------------------------------
\moderncvstyle{classic} % options: 'casual', 'classic', 'banking', 'oldstyle', 'fancy'
\moderncvcolor{black}   % monochrome look
\nopagenumbers{}        % remove page numbers

% If a thin rule is still desired under sections, keep your rule:
% \providecommand*{\sectionstylerule}{}
% \newcommand*{\sectionruleheight}{0.1pt} % set to 0pt to remove the line
% \renewcommand*{\sectionstylerule}{\par\vspace{0ex}\hrule height \sectionruleheight\relax}
% (you already defined \sectionstylerule)

% Remove left bars by redefining section style
\makeatletter
\renewcommand*{\sectionstyle}[1]{%
  \sectionfont\textcolor{color1}{#1}%
}
\makeatother


%----------------------------------------------------------
% Packages and formatting
%----------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.4em, itemsep=0.1em, topsep=1.5em, label=\textbullet} % round bullets
\setlist[itemize,2]{leftmargin=2.1em, itemsep=0.1em, topsep=0.6em, label=\textbullet}

% Add some vertical space between sections
\usepackage{etoolbox}
\patchcmd{\section}{\par\vspace{2.5ex}}{\par\vspace{3.8ex}}{}{}

% Make name more discrete and serious
\renewcommand*{\familydefault}{\sfdefault}
\renewcommand*{\namefont}{\Large\bfseries}
\renewcommand*{\titlefont}{\Large}
\renewcommand*{\sectionfont}{\large\bfseries}
\renewcommand*{\subsectionfont}{\normalsize\bfseries}


%----------------------------------------------------------
% Personal Information
%----------------------------------------------------------
\name{}{Guillermina Senn}
\email{senn.guillermina@gmail.com}
\homepage{guillerminasenn.github.io}
% \homepage{https://www.ntnu.edu/employees/guillermina.senn}

%----------------------------------------------------------
\begin{document}
\makecvtitle

%----------------------------------------------------------
\textbf{Research interests:} 
Computational statistics; scalable Monte Carlo methods; uncertainty quantification.
% \cvitem{Research interests}{Computational statistics; scalable Monte Carlo methods; uncertainty quantification.}

%----------------------------------------------------------
\section{Employment}
\cventry{Feb 2026--}{\normalfont Visiting Graduate Researcher}{\normalfont Indiana University}{\normalfont Bloomington}{\normalfont USA}
{Postdoctoral work on scalable Monte Carlo methods and theory, advised by Nathan Glatt-Holtz.}
\vspace{0.3cm}
\cventry{2015--2021}{\normalfont Several roles}{\normalfont Nokia}{\normalfont Córdoba, Argentina}{}{
\vspace{0.01em}
\begin{itemize}
  \item Data Scientist (2020--2021): Applied statistics and ML to operational problems in mobile networks within an international team. Example projects:
  \begin{itemize}
  \item Customer complaint prediction: Developed a model to predict customer complaintsusing a large, imbalanced dataset (n=100k, p=4000) with the current and past state of mobile network indicators. Methods: weighted random forests and XGBoost; prototype under test at departure.
  \item City Mobility Index: Developed a city-level Mobility Index for Argentine cities during COVID-19 using anonymized data from 250k subscribers. Methods: PCA and clustering; proof of concept delivered.
  \end{itemize}
 \item Operations Consultant (2018--2020): Was part of a team designing and implementing a custom analytics-based mobile network monitoring solution. My tasks involved data analysis (SQL, descriptive stats, clustering), client reporting, and system monitoring/troubleshooting (SQL, Python, Linux).
 \item Engineer (2015--2018): Performed software and hardware maintenance on mobile network equipment.
  % \item Field Manager (2015--2018): Managed ~10 field teams deploying 2G/3G/4G base stations.
\end{itemize}
}

%----------------------------------------------------------
\section{Education}
\cventry{2022--present}{\normalfont Ph.D. in Mathematical Sciences}{\normalfont NTNU}{\normalfont Trondheim, Norway}{}{
Advised by Håkon Tjelmeland. Thesis defense in August 2026.
\newline
Dissertation: \textit{Scalable Markov Chain Monte Carlo for Bayesian Inverse Problems with Gaussian Priors}. 
\newline
\newline
The thesis was motivated by a real-world inverse problem, seismic wavelet estimation from large-scale images. The work was carried out in close collaboration with industry researchers at bp, and later alongside academic collaborators from UCLA and Indiana University Bloomington. The solution involved scalable Bayesian methodology, that we successfully tested on real seismic data. The methodology was then extended to inverse problems with Gaussian priors in general.}
\vspace{0.3cm}
\cventry{2018--2021}{\normalfont M.S. in Applied Statistics}{\normalfont National University of Córdoba}{\normalfont Argentina}{}{
Advised by Monica Balzarini.
\newline 
Thesis title: \textit{Multicollinearity and Overfitting in Hierarchical Bayesian Models for Spatial Data. An application to Landscape-Scale Ecosystem Services Modeling.}
}
\vspace{0.3cm}
\cventry{2009--2016}{\normalfont Telecommunications Engineering}{\normalfont National Defense University}{\normalfont Córdoba, Argentina}{}{}

%----------------------------------------------------------
\section{Research Visits}
\cventry{2024--2025}{\normalfont Visiting Graduate Researcher}
{\normalfont Department of Biostatistics, Fielding School of Public Health, University of California, Los Angeles}{}{}{
  Worked on scalable Monte Carlo methods for high-dimensional inverse problems.
}
\cventry{Dec 2024}{\normalfont Visiting Graduate Researcher}
{\normalfont Department of Statistics, Indiana University Bloomington}{}{}{}
\cventry{Jan 2024}{\normalfont Visitor}{\normalfont bp's Research Center}{\normalfont London}{}{Visited bp's Research Center to collaborate on scalable Bayesian methods for seismic data analysis.}

%----------------------------------------------------------
\section{Publications}
\cvitem{Published}{
\vspace{-0.5cm}
\begin{itemize}
    \item Senn, G., N. Glatt-Holtz, G. Carigi, A. Holbrook, and H. Tjelmeland, (2026) \textit{Multiproposal Elliptical Slice Sampling}. Submitted to \textit{UAI 2026}.
    \item Senn, G., H. Tjelmeland, N. Glatt-Holtz, M. Walker, and A. Holbrook (2026) \textit{Bayesian Semi-Blind Deconvolution at Scale}. \textit{arXiv.}
    \item Senn, G., M. Walker, and H. Tjelmeland (2025). \textit{Scalable Bayesian seismic wavelet estimation.} \textit{Geophysical Prospecting.}
\end{itemize}
}
\vspace{0.3cm}
\cvitem{In preparation}{
\vspace{-0.5cm}
\begin{itemize}
\item Carigi, G., N. E. Glatt-Holtz, C. F. Mondaini, and G. Senn (2026). \textit{On the Mixing Properties
of Some Preconditioned Multiproposal Markov Chain Monte Carlo Algorithms}. 
\end{itemize}
}

%----------------------------------------------------------
\section{Presentations}
\cvitem{}{\scriptsize \textsf{I}=Invited talk; \textsf{C}=contributed talk; \textsf{P}=poster}
\cvitem{Conferences}{
\vspace{-0.5cm}
\begin{itemize}
    \item 2026. \textit{Multiproposal Elliptical Slice Sampling.} SIAM UQ. Minneapolis, USA. {\scriptsize (\textsf{I})}
  \item 2025. \textit{Scalable Bayesian seismic wavelet estimation.} Lofoten Seminar in Applied Geophysics. {\scriptsize (\textsf{C})}
  \item 2025. \textit{Scalable MCMC for Bayesian blind deconvolution.} BayesComp, Singapore. {\scriptsize (\textsf{P})}
  \item 2024. \textit{Spatial Bayesian seismic wavelet estimation from seismic volumes and well data.} Geostats, Ponta Delgada, Azores. {\scriptsize (\textsf{C})}
\end{itemize}
}
\vspace{0.3cm}
\cvitem{Seminars}{
\vspace{-0.5cm}
\begin{itemize}
  \item 2025. \textit{Scalable Bayesian seismic wavelet estimation.} SINTEF Industri, Trondheim. {\scriptsize (\textsf{I})}
  \item 2024. \textit{Bayesian seismic wavelet and subsurface estimation via Gibbs sampling on a cyclic domain.} Department of Statistics, Indiana University Bloomington. {\scriptsize (\textsf{I})}
\end{itemize}
}

%----------------------------------------------------------
\section{Teaching Experience}
\cvitem{}{
\vspace{-0.5cm}
\begin{itemize}
  \item Fall 2025. \href{https://www.ntnu.edu/studies/courses/TMA4115\#tab=omEmnet}{TMA4115 Mathematics 3 (Linear Algebra)}. NTNU. Substitute instructor.
  \item Fall 2025. \href{https://www.ntnu.edu/studies/courses/ISTT1001\#tab=omEmnet}{ISTX1001 Industrial Statistics}. NTNU. TA.
  \item Fall 2024. \href{https://www.ntnu.edu/studies/courses/TMA4240\#tab=omEmnet}{TMA4240 Statistics}. NTNU. TA.
  \item Fall 2024, Fall 2023, Fall 2022. \href{https://www.ntnu.edu/studies/courses/ST1201\#tab=omEmnet}{ST1201/ST6201 Statistical Methods}. NTNU. TA with teaching responsibilities.
  \item Spring 2024, Spring 2023. \href{https://www.ntnu.edu/studies/courses/TMA4300\#tab=omEmnet}{TMA4300 Computer Intensive Statistical Methods}. NTNU. TA.
  \item Spring 2022. \href{https://www.ntnu.edu/studies/courses/TMA4255\#tab=omEmnet}{TMA4255 Applied Statistics}. NTNU. TA and exercise sessions instructor.
\end{itemize}
}

%----------------------------------------------------------
\section{Service}
% \cvitem{2023--2025}{\normalfont "Working Group in Statistical Sciences" seminar co-organizer, Department of Mathematical Sciences, NTNU, Trondheim.}
\cventry{2023--2025}{\normalfont Seminar co-organizer}{\normalfont Department of Mathematical Sciences, NTNU}{\normalfont Trondheim}{}{
Co-organized the "Working Group in Statistical Sciences" seminar series, which included inviting PhD/postdoc speakers, scheduling and hosting talks.}
\vspace{0.3cm}
\cventry{Apr 2020--Jul 2020}{\normalfont Student Volunteer}{\normalfont National University of Córdoba}{\normalfont Cordoba}{\normalfont Argentina}{
Contributed to weekly reports analyzing COVID-19 data for the Córdoba province as part of a departmental consultancy for the provincial government.
}

%----------------------------------------------------------
\section{Other Skills}
\cvitem{Languages}{English, Spanish, Norwegian, German.}
\vspace{0.3em}
\cvitem{Computing}{Python, R, SQL, bash scripting, Linux, HPC, Git.}

% %----------------------------------------------------------
% \newpage
% \section{References}
% \cvitem{}{
% \begin{itemize}
%     \item \textbf{Håkon Tjelmeland} \href{mailto:haakon.tjelmeland@ntnu.no}{haakon.tjelmeland@ntnu.no} (PhD advisor).
%     \item \textbf{Nathan Glatt-Holtz} \href{mailto:negh@iu.edu}{negh@iu.edu} (Postdoc advisor).
%     \item \textbf{Andrew Holbrook} \href{mailto:aholbroo@g.ucla.edu}{aholbroo@g.ucla.edu} (Hosted at UCLA).
%     \item \textbf{Andrew Holbrook} \href{mailto:aholbroo@g.ucla.edu}{aholbroo@g.ucla.edu} (Hosted at UCLA).
% \end{itemize}
% }

\end{document}
