\documentclass[12pt,a4paper]{moderncv}

%----------------------------------------------------------
% Style configuration
%----------------------------------------------------------
\moderncvstyle{classic} % options: 'casual', 'classic', 'banking', 'oldstyle', 'fancy'
\moderncvcolor{black}   % monochrome look
\nopagenumbers{}        % remove page numbers

%----------------------------------------------------------
% Packages and formatting
%----------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.2em, itemsep=0.35em, topsep=0.4em, label=-} % smaller, cleaner bullets

% Add some vertical space between sections
\usepackage{etoolbox}
\patchcmd{\section}{\par\vspace{2.5ex}}{\par\vspace{3.8ex}}{}{}

% Make name more discrete and serious
\renewcommand*{\namefont}{\large\bfseries}
\renewcommand*{\titlefont}{\large\bfseries}

%----------------------------------------------------------
% Personal Information
%----------------------------------------------------------
\name{}{Guillermina Senn}
\email{guillermina.senn@ntnu.no, senng@iu.edu}
\homepage{guillerminasenn.github.io}
% \homepage{https://www.ntnu.edu/employees/guillermina.senn}

%----------------------------------------------------------
\begin{document}
\makecvtitle

%----------------------------------------------------------
\section{Research Interests}
Computational statistics; scalable Monte Carlo methods; uncertainty quantification.

%----------------------------------------------------------
\section{Employment}
\cventry{Feb 2026--Jul 2026}{Visiting Graduate Researcher}{Indiana University}{Bloomington}{USA}{Postdoctoral work on scalable Monte Carlo methods and theory, advised by Nathan Glatt-Holtz.}
\vspace{0.3cm}
\cventry{2015--2021}{Several Roles}{Nokia}{Córdoba, Argentina}{}{
Worked in the deployment of mobile networks in Argentina, Uruguay, and Paraguay, first as an engineer, then as analytics consultant, and finally as data scientist.
% In my last role, I used statistics and machine learning to aid the customer’s mobile network operation.
}

%----------------------------------------------------------
\section{Education}
\cventry{2022--present}{Ph.D. in Mathematical Sciences}{NTNU}{Trondheim, Norway}{}{
Dissertation: \textit{Scalable Markov Chain Monte Carlo for Bayesian Inverse Problems with Gaussian Priors}. Advised by Håkon Tjelmeland. Expected June 2026.}
\vspace{0.3cm}
\cventry{2018--2021}{M.S. in Applied Statistics}{National University of Córdoba}{Argentina}{}{}
\vspace{0.3cm}
\cventry{2009--2016}{Telecommunications Engineering}{National Defense University}{Córdoba, Argentina}{}{}

%----------------------------------------------------------
\section{Research Visits}
\cventry{2024--2025}{Visiting Graduate Researcher}{Department of Biostatistics, Fielding School of Public Health, University of California, Los Angeles}{}{}{}

%----------------------------------------------------------
\section{Publications}
\cvitem{Published}{
\vspace{-0.5cm}
\begin{itemize}
    \item Senn, G., N. Glatt-Holtz, G. Carigi, A. Holbrook, and H. Tjelmeland, (2026) \textit{Multiproposal Elliptical Slice Sampling}. \textit{arXiv.}
    \item Senn, G., H. Tjelmeland, N. Glatt-Holtz, M. Walker, and A. Holbrook (2026) \textit{Bayesian Semi-Blind Deconvolution at Scale}. \textit{arXiv.}
    \item Senn, G., M. Walker, and H. Tjelmeland (2025). \textit{Scalable Bayesian seismic wavelet estimation.} \textit{Geophysical Prospecting.}
\end{itemize}
}
\vspace{0.3cm}
\cvitem{To appear}{
\vspace{-0.5cm}
\begin{itemize}
\item Carigi, G., N. E. Glatt-Holtz, C. F. Mondaini, and G. Senn (2026). \textit{On the Mixing Properties
of Some Preconditioned Multiproposal Markov Chain Monte Carlo Algorithms}. 
\end{itemize}
}

%----------------------------------------------------------
\section{Presentations}
\cvitem{Conferences}{
\vspace{-0.5cm}
\begin{itemize}
    \item 2026. \textit{Multiproposal Elliptical Slice Sampling (invited talk).}  SIAM UQ. Minneapolis, USA.
  \item 2025. \textit{Scalable Bayesian seismic wavelet estimation.} Lofoten Seminar in Applied Geophysics.
  \item 2025. \textit{Scalable MCMC for Bayesian blind deconvolution (poster).} BayesComp, Singapore.
  \item 2024. \textit{Spatial Bayesian seismic wavelet estimation from seismic volumes and well data.} Geostats, Ponta Delgada, Azores.
\end{itemize}
}
\vspace{0.3cm}
\cvitem{Seminars}{
\vspace{-0.5cm}
\begin{itemize}
  \item 2025. \textit{Scalable Bayesian seismic wavelet estimation (invited talk).} SINTEF Industri, Trondheim.
  \item 2024. \textit{Bayesian seismic wavelet and subsurface estimation via Gibbs sampling on a cyclic domain (invited talk).} Department of Statistics, Indiana University Bloomington.
\end{itemize}
}

%----------------------------------------------------------
\section{Teaching Experience}
\cvitem{}{
\vspace{-0.5cm}
\begin{itemize}
  \item \href{https://www.ntnu.edu/studies/courses/TMA4115#tab=omEmnet}{\textbf{TMA4115 Mathematics 3 (Linear Algebra)}} (Fall 2025), NTNU — with teaching, substitute.
  \item \href{https://www.ntnu.edu/studies/courses/ISTT1001#tab=omEmnet}{\textbf{ISTX1001 Industrial Statistics}} (Fall 2025), NTNU — TA.
  \item \href{https://www.ntnu.edu/studies/courses/TMA4240#tab=omEmnet}{\textbf{TMA4240 Statistics}} (Fall 2024), NTNU — TA.
  \item \href{https://www.ntnu.edu/studies/courses/ST1201#tab=omEmnet}{\textbf{ST1201/ST6201 Statistical Methods}} (Fall 2024, Fall 2023, Fall 2022), NTNU — TA with teaching responsibilities.
  \item \href{https://www.ntnu.edu/studies/courses/TMA4300#tab=omEmnet}{\textbf{TMA4300 Computer Intensive Statistical Methods}} (Spring 2024, Spring 2023), NTNU — TA.
  \item \href{https://www.ntnu.edu/studies/courses/TMA4255#tab=omEmnet}{\textbf{TMA4255 Applied Statistics}} (Spring 2022), NTNU — TA and instructor for exercise sessions.
\end{itemize}
}

%----------------------------------------------------------
\section{Service}
\cvitem{2023--2025}{"Working Group in Statistical Sciences" seminar co-organizer, Department of Mathematical Sciences, NTNU, Trondheim.}

%----------------------------------------------------------
\section{Other Skills}
\cvitem{Languages}{English, Spanish, Norwegian, German.}
\cvitem{Computing}{Python, R, SQL, bash scripting, Linux, HPC, Git.}

% %----------------------------------------------------------
% \newpage
% \section{References}
% \cvitem{}{
% \begin{itemize}
%     \item \textbf{Håkon Tjelmeland} \href{mailto:haakon.tjelmeland@ntnu.no}{haakon.tjelmeland@ntnu.no} (PhD advisor).
%     \item \textbf{Nathan Glatt-Holtz} \href{mailto:negh@iu.edu}{negh@iu.edu} (Postdoc advisor).
%     \item \textbf{Andrew Holbrook} \href{mailto:aholbroo@g.ucla.edu}{aholbroo@g.ucla.edu} (Hosted at UCLA).
%     \item \textbf{Andrew Holbrook} \href{mailto:aholbroo@g.ucla.edu}{aholbroo@g.ucla.edu} (Hosted at UCLA).
% \end{itemize}
}

\end{document}
